%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{About Me}
  \begin{itemize}[<+->]
  \item Working with Dan Roth since August 2013.
  %% \item Work on machine learning and NLP.
  \item Publications
    \begin{itemize}[<+->]
    \item \emph{Learning with Amortized Inference} \\
      (with Chang, Kundu, Roth) AAAI'15.
    \item \emph{Understanding Mathematical Relations in Text} \\
      (with Roy, Roth) Submitted to TACL'15.
      \end{itemize}
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \begin{center}
    {
      \huge Grounding Events to a Knowledge Base
    } \\
    (current work)
  \end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{The Problem}

  \begin{exampleblock}{Example}
      {The {\color<3->{red} battle}\only<4->{$\implies$ (Battle of Trafalgar)} was the most decisive naval victory of the {\color<3->{red}war}\only<4->{$\implies$ (Napoleanic Wars)}}. The British led by Admiral Lord Nelson defeated the French off the coast of Spain. Nelson succumbed to his injuries in battle.
      \end{exampleblock}
  \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Motivation}
  \begin{itemize}[<+->]
  \item Event mentions in a text display variability and ambiguity.
    \begin{exampleblock}{Variability}
      {Battle of Waterloo, defeat at Waterloo, campaign of Waterloo, the 1815 battle, Napolean's defeat, French cavalry attack}
    \end{exampleblock}
    \begin{exampleblock}{Ambiguity}
     At the {\color<3->{red} Olympics } in Athens, Greece, Kupets won a silver medal with her fellow U.S. team members in the team all-around competition.
    \end{exampleblock}
  \item Understanding events is difficult - Coherence.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Benefits}
  \begin{itemize}
  \item More context! - \onslide<2->{event coreference, news aggregation etc.}
  \end{itemize}
  \onslide<3->
  \begin{block}{Entity Wikification}
    Following {\color<4>{blue} restoration} of the monarchy under \highlightchunk{red}{Charles}, Taylor emigrated to the ...
    %% After the {\color<3>{blue} death of \highlightchunk{red}{Cromwell}}, \highlightchunk{red}{Charles'} chances of regaining the Crown at first seemed slim as Cromwell was succeeded as Lord Protector by his son, Richard.
  \end{block}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Comparison with Entity Wikification}
  \begin{itemize}[<+->]
  \item \emph{Scarcity of training data}: Only 1\% of wikipedia pages are about events.
    %% Number higher if you consider events in subheading of an entity's page (eg. ``Invasion of Russia'' section under the wikipage of \textsc{Napolean}).
  %% \item Detection of Event Mention.
    %% Mentions are not as specific. "Chicago" vs "the civil war".
  %% \item {\color{red}solution:} Dynamic mention expansion.
  \item Non-Trivial Candidate Generation.
    %% is not as trivial as dictionary look-up.
  %% \item {\color{red}solution:} Cascaded filtering.
  \item \textsc{Status:} Current system gets 62\% F1 on events in wikipedia.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \begin{frame}

%%   \begin{block}{Problem}
%%     Candidate generation is not as trivial as dictionary look-up.
%%   \end{block}

%%   \begin{exampleblock}{Possible Solution}
%%     Cascaded filtering
%%   \end{exampleblock}

%%   \begin{block}{Problem}
%%     Mentions are not as specific. "Chicago" vs "the civil war".
%%   \end{block}

%%   \begin{exampleblock}{Possible Solution}
%%     Cascaded filtering
%%   \end{exampleblock}

%% \end{frame}
